Single Site, Single Disturbance

### 2020-10-04 SingleSite_SingleDisturb.Rmd
flushing out to-do more

## Todo
-   Tweak model to have a simple C budget -- where does the C go when the model doesn't assimilate disturbance?
-   Apply to SIPNET SDA

>>>>

## Todo
-   Move forecast out of JAGS
-   Tweak model to have a simple C budget -- where does the C go when the model doesn't assimilate disturbance?
-   Apply to SIPNET SDA
-   Calibrate state and transition probabilities for a single region
-   Upgrade code to multinomial
-   Add PFT switching
-   Add ensemble weighting so that we can manage ensemble sizes
-   Add "fusion" if a case becomes too rare to worry about
-   Think about whether we need to add LULC state to state variables & how LULC state would be assimilated
-   Test against subseasonal dynamics (e.g. distinguishing phenology from disturbance)
-   investigate whether we need a "jumpback" capacity once disturbance event type and timing is resolved
-
